Title Goes Here

### 2025-04-21 analysis/supplementary-materials/appendix1.qmd
Plots in main paper improved. Removed Cu from the PCA analysis

# Read individual xrd files
sp6_xrd <- read_csv('data/xrd_data/SP6_xrd.csv')
sp7_xrd <- read_csv('data/xrd_data/SP7_xrd.csv')
sp10_xrd <- read_csv('data/xrd_data/SP10_xrd.csv')
sp14_xrd <- read_csv('data/xrd_data/SP14_xrd.csv')
sp18_xrd <- read_csv('analysis/data/raw_data/xrd_data/SP18_xrd.csv')
sp21_xrd <- read_csv('data/xrd_data/SP21_xrd.csv')
sp28_xrd <- read_csv('data/xrd_data/SP28_xrd.csv')
sp30_xrd <- read_csv('data/xrd_data/SP30_xrd.csv')
sp33_xrd <- read_csv('data/xrd_data/SP33_xrd.csv')
sp34_xrd <- read_csv('data/xrd_data/SP34_xrd.csv')
sp40_xrd <- read_csv('data/xrd_data/SP40_xrd.csv')
sp50_xrd <- read_csv('data/xrd_data/SP50_xrd.csv')
sp52_xrd <- read_csv('data/xrd_data/SP52_xrd.csv')
sp57_xrd <- read_csv('data/xrd_data/SP57_xrd.csv')
sp59_xrd <- read_csv('data/xrd_data/SP59_xrd.csv')
sp61_xrd <- read_csv('data/xrd_data/SP61_xrd.csv')
sp63_xrd <- read_csv('data/xrd_data/SP63_xrd.csv')
sp66_xrd <- read_csv('data/xrd_data/SP66_xrd.csv')

@@

>>>>

# Read individual xrd files
sp6_xrd <- read_csv('data/xrd_data/SP6_xrd.csv')
sp7_xrd <- read_csv('data/xrd_data/SP7_xrd.csv')
sp10_xrd <- read_csv('data/xrd_data/SP10_xrd.csv')
sp14_xrd <- read_csv('data/xrd_data/SP14_xrd.csv')
sp18_xrd <- read_csv('analysis/data/raw_data/xrd_data/SP18_xrd.csv')
sp21_xrd <- read_csv('data/xrd_data/SP21_xrd.csv')
sp28_xrd <- read_csv('data/xrd_data/SP28_xrd.csv')
sp30_xrd <- read_csv('data/xrd_data/SP30_xrd.csv')
sp33_xrd <- read_csv('data/xrd_data/SP33_xrd.csv')
sp34_xrd <- read_csv('data/xrd_data/SP34_xrd.csv')
sp40_xrd <- read_csv('data/xrd_data/SP40_xrd.csv')
sp50_xrd <- read_csv('data/xrd_data/SP50_xrd.csv')
sp52_xrd <- read_csv('data/xrd_data/SP52_xrd.csv')
sp57_xrd <- read_csv('data/xrd_data/SP57_xrd.csv')
sp59_xrd <- read_csv('data/xrd_data/SP59_xrd.csv')
sp61_xrd <- read_csv('data/xrd_data/SP61_xrd.csv')
sp62_xrd <- read_csv('analysis/data/raw_data/xrd_data/SP62_xrd.csv')
sp63_xrd <- read_csv('data/xrd_data/SP63_xrd.csv')
sp66_xrd <- read_csv('data/xrd_data/SP66_xrd.csv')

@@

```{r}
#| label: fig-xrd-sp62
#| fig-cap: Plot of minerals identified through XRD in the Middle Jurassic (Malhão formation) chert sample from the outcrop Oliveiras (SP7_CSV). The rhombus shape signifies main peaks key to identify each mineral. Labels represent the d spacing values of key mineral peaks.

# SP62 Oliveiras
sp62_marks <- xrd_marks |> 
  filter(Sample == "SP62")
sp62_perc <- xrd_perc |> 
  filter(Sample == "SP62") |> 
  select(-Sample, -ESD)

sp62_plot <- sp62_xrd |> 
  dplyr::mutate(Difference = Observed - Calculated - 3000) |> 
  select(-Quartz_nb) |> 
  pivot_longer(cols = c(Difference, Background, Observed, Quartz), 
               names_to = "Phase", 
               values_to = "Count") |> 
  mutate(Phase = factor(Phase, levels = c("Observed", "Quartz", "Background", "Difference"))) |>
  ggplot(aes(x = Angle, y = Count, colour = Phase)) +
  geom_line(linewidth = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity (counts)") +
  theme_minimal() +
  coord_cartesian(ylim = c(-5000, 50000)) +
  geom_point(data = sp62_marks, aes(x = Angle, y = Intensity + 600, colour = Phase), size = 3, shape = 18) +
  geom_label(data = sp62_marks, aes(x = Angle, y = Intensity, label = d), 
            size = 3, fill = "white", label.size = 0.2, vjust = -1, show.legend = FALSE) +
  scale_colour_manual(values = c("lightsteelblue3", "salmon", "orchid","snow4")) +
  annotate(geom = "table", x = 75, y = 50000, label = list(cbind(sp62_perc)))
